---
title: "Mini Data Analysis Milestone 2"
output: github_document
---

*To complete this milestone, you can either edit [this `.rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-2.Rmd) directly. Fill in the sections that are commented out with `<!--- start your work here--->`. When you are done, make sure to knit to an `.md` file by changing the output in the YAML header to `github_document`, before submitting a tagged release on canvas.*

# Welcome to the rest of your mini data analysis project!

In Milestone 1, you explored your data. and came up with research questions. This time, we will finish up our mini data analysis and obtain results for your data by: 

- Making summary tables and graphs 
- Manipulating special data types in R: factors and/or dates and times.
-   Fitting a model object to your data, and extract a result.
-   Reading and writing data as separate files.

We will also explore more in depth the concept of *tidy data.* 

**NOTE**: The main purpose of the mini data analysis is to integrate what you learn in class in an analysis. Although each milestone provides a framework for you to conduct your analysis, it's possible that you might find the instructions too rigid for your data set. If this is the case, you may deviate from the instructions -- just make sure you're demonstrating a wide range of tools and techniques taught in this class.

# Instructions

**To complete this milestone**, edit [this very `.Rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-2.Rmd) directly. Fill in the sections that are tagged with `<!--- start your work here--->`.

**To submit this milestone**, make sure to knit this `.Rmd` file to an `.md` file by changing the YAML output settings from `output: html_document` to `output: github_document`. Commit and push all of your work to your mini-analysis GitHub repository, and tag a release on GitHub. Then, submit a link to your tagged release on canvas.

**Points**: This milestone is worth 50 points: 45 for your analysis, and 5 for overall reproducibility, cleanliness, and coherence of the Github submission. 

**Research Questions**: In Milestone 1, you chose two research questions to focus on. Wherever realistic, your work in this milestone should relate to these research questions whenever we ask for justification behind your work. In the case that some tasks in this milestone don't align well with one of your research questions, feel free to discuss your results in the context of a different research question.

# Learning Objectives

By the end of this milestone, you should:

-   Understand what *tidy* data is, and how to create it using `tidyr`.
-   Generate a reproducible and clear report using R Markdown.
-   Manipulating special data types in R: factors and/or dates and times.
-   Fitting a model object to your data, and extract a result.
-   Reading and writing data as separate files.

# Setup

Begin by loading your data and the tidyverse package below:

```{r, message = FALSE}
library(datateachr) # <- might contain the data you picked!
library(tidyverse)
library(dplyr)
library(ggplot2)
library(broom)
library(readr)
library(here)
```

# Task 1: Process and summarize your data 

From milestone 1, you should have an idea of the basic structure of your dataset (e.g. number of rows and columns, class types, etc.). Here, we will start investigating your data more in-depth using various data manipulation functions. 

### 1.1 (1 point) 

First, write out the 4 research questions you defined in milestone 1 were. This will guide your work through milestone 2:

<!-------------------------- Start your work below ---------------------------->

1. *Question 1: How many cherry trees are there Vancouver west and Vancouver east?* - Answered this question in the first summarizing activity - I add to it in it's section to include differences in planting times between the areas.

2. *Question 2: Which neighborhood has the highest density of each of the cherry tree species?* - This question was changed to - *What is the relationship between location and common cherry tree diameter?* - I thought that the new question would give me the opportunity to answer questions using the more numerical side of the data set.

3. *Question 3: Is there a relationship between the location of the cherry trees and their height?* slightly changed this question to - *In which area are trees larger? Vancouver east or Vancouver west?.* I did this because the height ID variable did not seem to be continuous.

4. *Question 4: Is there a geographical area of Vancouver where the city planted more cherry trees? If so, does it differ by decade?*

<!----------------------------------------------------------------------------->

Here, we will investigate your data using various data manipulation and graphing functions.

### 1.2 (8 points)

Now, for each of your four research questions, choose one task from options 1-4 (summarizing), and one other task from 4-8 (graphing). You should have 2 tasks done for each research question (8 total). Make sure it makes sense to do them! (e.g. don't use a numerical variables for a task that needs a categorical variable.). Comment on why each task helps (or doesn't!) answer the corresponding research question.

Ensure that the output of each operation is printed!

Also make sure that you're using dplyr and ggplot2 rather than base R. Outside of this project, you may find that you prefer using base R functions for certain tasks, and that's just fine! But part of this project is for you to practice the tools we learned in class, which is dplyr and ggplot2.

**Summarizing:**

1.  Compute the *range*, *mean*, and *two other summary statistics* of **one numerical variable** across the groups of **one categorical variable** from your data.

2.  Compute the number of observations for at least one of your categorical variables. Do not use the function `table()`!

3.  Create a categorical variable with 3 or more groups from an existing numerical variable. You can use this new variable in the other tasks! *An example: age in years into "child, teen, adult, senior".*

4. Compute the proportion and counts in each category of one categorical variable across the groups of another categorical variable from your data. Do not use the function `table()`!
**Graphing:**
6. Create a graph of your choosing, make one of the axes logarithmic, and format the axes labels so that they are "pretty" or easier to read.
7. Make a graph where it makes sense to customize the alpha transparency.

Using variables and/or tables you made in one of the "Summarizing" tasks: 

8. Create a graph that has at least two geom layers. 
9. Create 3 histograms, with each histogram having different sized bins. Pick the "best" one and explain why it is the best.

Make sure it's clear what research question you are doing each operation for!

<!------------------------- Start your work below ----------------------------->
**Question 4: Is there a geographical area of Vancouver where the city planted more cherry trees? If so, does it differ by decade?**
To start off, I need to put the common Vancouver cherry trees together. I chose the 8 most common cherry trees. This is so that there would be enough data points for each species throughout the analysis. 
```{r}
com_cherry <- vancouver_trees %>% 
  filter(common_name %in% c("KWANZAN FLOWERING CHERRY", "AKEBONO FLOWERING CHERRY", "SCHUBERT CHOKECHERRY", "PINK PERFECTION CHERRY", "JAPANESE FLOWERING CHERRY", "HIGAN CHERRY", "MAZZARD CHERRY", "RANCHO SARGENT CHERRY"))

print(com_cherry)
```
**Summarizing** (4.Compute the proportion and counts in each category of one categorical variable across the groups of another categorical variable from your data. Do not use the function `table()`!)
```{r}
freq_cher <- com_cherry %>%
  group_by(common_name, neighbourhood_name) %>%
  summarise(n = n(), .groups = "drop_last") %>%
  mutate(freq = n / sum(n))

print(freq_cher)
```
The above I calculated the frequency of each of the the 8 most common species of cherry trees in Vancouver by neighbourhood name. 

**Graphing** (8. Create a graph that has at least two geom layers.)

Now for graphing I'm going to look at how the species planted may differ over time. Attempting to answer the second half of Question 4, regarding time.
```{r}
cher_box <- com_cherry %>%
  ggplot( aes(x = common_name, y = date_planted, fill = common_name)) +
    geom_violin(width=2.0) +
    geom_boxplot(width=0.5, alpha=0.2) +
    ylab("Date Planted") +
    xlab("Common Name") +
    ggtitle("Common Cherry Trees Species in Vancouver", subtitle = "by date planted" ) +
            theme(axis.text.x = element_text(angle = 90, size = 0), legend.key.size = unit(0.5, "cm"))

print(cher_box)
```

Above I utilized 2 types of geoms, geom_box plot() and geom_violin().

Combining these two geoms makes it easy to visualize when the most common cherry trees in Vancouver were planted for those we have planting data on. 

**Question 3: Is there a relationship between the location of the cherry trees and their height?**

**Summarizing** (3. Create a categorical variable with 3 or more groups from an existing numerical variable. You can use this new variable in the other tasks! *An example: age in years into "child, teen, adult, senior")
```{r}
cherry_area <- com_cherry %>% mutate(area = case_when(
  neighbourhood_name %in% c("ARBUTUS-RIDGE", "DOWNTOWN", "FAIRVIEW", "DUNBAR-SOUTHLANDS", "KERRISDALE", "SHAUGHNESSY", "MARPOLE", "OAKRIDGE", "SOUTH CAMBIE", "KITSILANO", "WEST POINT GREY", "WEST END") ~'van_west', TRUE ~ 'van_east')) %>% 
  arrange(area)

glimpse(cherry_area)
```

Above I used the mutate() dplyr function to divide neighbourhood names into their respective areas (Vancouver west & Vancouver east). This did not make sense for me to do with a numerical variable with my data set and what I wanted to do. 
```{r}
van_west <- as_tibble(cherry_area) %>%
filter(area == "van_west") %>%
  select(date_planted, common_name, area)
van_west

van_east <- as_tibble(cherry_area) %>%
filter(area == "van_east") %>%
  select(date_planted, common_name, area)
van_east
```
Instead of using the height_id for the trees I decided to use the diameter. The height ID value seems to have less variation between different tree types.

My new question would be: **In which area are trees larger? Vancouver east or Vancouver west?.**

**Graphing** (7. Make a graph where it makes sense to customize the alpha transparency)
```{r}
dia_cherry<-ggplot(cherry_area, aes(x = diameter, fill = area)) +
  geom_density(colour= "black", alpha = 0.65) +
  labs(title = "Diameter of common cherry tree species by area", fill = "Area") + 
  scale_x_continuous(name="Tree Diameter", limits=c(0, 50)) +
  scale_y_continuous(name="Density", limits=c(0, 0.06)) 
  
print(dia_cherry)
```

I customized alpha transparency in the density plot so that you could properly see both areas (Vancouver west & Vancouver east).

**Question 1: How many cherry trees are there Vancouver west and Vancouver east?**

**Summarizing** (2.  Compute the number of observations for at least one of your categorical variables. Do not use the function `table()`!)
```{r}
no_area <- cherry_area %>% 
  group_by(area) %>% 
  summarise(Count = n())

print(no_area)
```
Above I calculated the number of the 8 most common cherry trees for the areas of Vancouver west and Vancouver east. In doing this I can see that there are slightly more trees in the neighborhoods which make up Vancouver east than there in in Vancouver west. 

In doing the above count I answered my first question. So, for the graphing part I will investigate further and see if there in a difference in between the number of the 8 most common cherry tress planted by planting year.  
```{r}
cher_dat <- cherry_area %>% 
  mutate(Month = month(date_planted, label = TRUE), Year = year (ymd(date_planted)))

glimpse(cher_dat)
```
In the above used the mutate() function to create new categories for the month and year and stored them in cher_dat, which I then used the glimpse() function to double check that I did correctly. 

**Graphing** (9. Create 3 histograms, with each histogram having different sized bins. Pick the "best" one and explain why it is the best)

First histogram binwidth:
```{r}
hist1 <- ggplot(cher_dat, aes(x = Year, fill = area, color= area)) +
  geom_histogram(position = "identity", alpha = 0.5, bins = 30)

print(hist1)
```

Second histogram binwidth:
```{r}
hist2 <- ggplot(cher_dat, aes(x = Year, fill = area, color = area)) +
  geom_histogram(position = "identity", alpha = 0.5, bins = 15)

print(hist2)
```

Third binwidth:
```{r}
hist3 <- ggplot(cher_dat, aes(x = Year, fill = area, color = area)) +
  geom_histogram(position="identity", alpha = 0.5, bins= 25)

print(hist3)
```

I think that the third binwidth (bins= 25) makes the most sense for this histogram, as histogram 3 is easy to read, includes all data points in the count, many of the bins land close to count lines. 

**Question 2: Which neighborhood has the highest density of each of the cherry tree species?**
I've decided to change question 2 to remove its similarity from former questions that have been asked in this data set. Instead I would like to change the question to something that lets me examine more of the numerical variables in my data set. New question: **What is the relationship between location and common cherry tree diameter?** 

**Summarizing** (1.  Compute the *range*, *mean*, and *two other summary statistics* of **one numerical variable** across the groups of **one categorical variable** from your data.) 

Below I compute the summary stats of mean, standard deviation and the median of numerical variable diameter in regards to the categorical variable of common name - which is filtered to show the 8 most common cherry trees in Vancouver.
```{r}
mean_sd_med <- cherry_area %>%  
  drop_na(diameter) |> 
  summarise(dia_mean = mean(diameter),
            dia_std = sd(diameter),
            dia_med = median(diameter))
print(mean_sd_med)
```
Below I calculate the range of the diameter for the the 8 most common cherry trees in Vancouver. Finding out the min and max gives me the diameter range.
```{r}
min_max <- cherry_area %>%  
  drop_na(diameter) |> 
  summarise(dia_min = min(diameter),
            dia_max = max(diameter))
print(min_max)
```

**Graphing** (6. Create a graph of your choosing, make one of the axes logarithmic, and format the axes labels so that they are "pretty" or easier to read.)

Below I create a scatter plot using ggplot2's geom_point() layer and I combine it with the geom_smooth() layer to show the relationship between diameter and longitude of common cherry tree species better. For an overall view of the relationship the x-axis was made logarithmic. 
```{r}
scatter_cher <- ggplot(cherry_area, aes(x = diameter, y = longitude)) +
  geom_point(shape = ".") +
  geom_smooth(method=lm) +
  scale_x_log10() +
  xlab("Tree Diameter") +
  ylab("Longitude") + 
  ggtitle("Relationship between diameter and longitude for cherry trees", subtitle = "For the 8 most common cherry tree species in Vancouver")

print(scatter_cher)
```

<!----------------------------------------------------------------------------->

### 1.3 (2 points)

Based on the operations that you've completed, how much closer are you to answering your research questions? Think about what aspects of your research questions remain unclear. Can your research questions be refined, now that you've investigated your data a bit more? Which research questions are yielding interesting results?

<!------------------------- Write your answer here
---------------------------->

 I think that I have gotten closer to answering some of my research questions. Question 1 I was surprisingly able to answer quite fast, and had to tweak my question for the graphing portion to find out more information. Question 4 is yielding some interesting results, with a clear difference between when different types of common species of cherry trees were planted in Vancouver. I would like to dive deeper into this question to potentially reveal if this differs by neighborhood/ area as well. While investigating the data I think that it is inevitable that new questions will come up and you will reassess your original questions with the more knowledge you have. A good example of this is that I had to refine my Question 3, since the height_range_id column of the data set turned out not to be ideal for graphing. While I am also very interested in the results from Question 2, the graph in particular make it look like there is a relationship between diameter and longitude. 

<!----------------------------------------------------------------------------->

# Task 2: Tidy your data 

In this task, we will do several exercises to reshape our data. The goal here is to understand how to do this reshaping with the `tidyr` package.

A reminder of the definition of *tidy* data:

-   Each row is an **observation**
-   Each column is a **variable**
-   Each cell is a **value**

### 2.1 (2 points)

Based on the definition above, can you identify if your data is tidy or untidy? Go through all your columns, or if you have \>8 variables, just pick 8, and explain whether the data is untidy or tidy.

<!--------------------------- Start your work below --------------------------->

The vancouver_trees data set from the datateachr() package is tidy data. My reasoning for vancouver_trees being tidy data is that it fits the description of tidy data - "each row had an observation, each column is a variable and each cell is a value". Vancouver_trees doesn't contain characteristics of an untidy data set such as a single variable across multiple columns or a single observation across multiple rows.

<!----------------------------------------------------------------------------->

### 2.2 (4 points)

Now, if your data is tidy, untidy it! Then, tidy it back to it's original state.

If your data is untidy, then tidy it! Then, untidy it back to it's original state.

Be sure to explain your reasoning for this task. Show us the "before" and "after".

<!--------------------------- Start your work below --------------------------->
First I will untidy the vancouver_trees data below. I will do this using the pivot_wider tidyverse function. 
```{r}
untidy <- vancouver_trees %>% 
  pivot_wider(id_cols = neighbourhood_name, names_from = diameter, values_from = height_range_id, 
              values_fn = length)
print(untidy)
```
The above untidy version of the data set vancouver_trees lets me get a better idea of which neighborhoods have complete height and diameter values, and how many complete sets of these values there are in my data set. As I was going through the cherry data I found that alot of the height_range_id data was missing. 

To clarify the above data is untidy because it has diameter observations as columns. 

Now I will tidy the data set vancouver_trees back to its original form. I will do this using the pivot_longer tidyverse function. 
```{r}
tidy <- untidy %>%
  pivot_longer(cols = c(-neighbourhood_name), names_to = "diameter",
               values_to = "height_range_id")
print(tidy)
```
Above I tidied the data back to original form with diameter and height range ID as columns with each row having an observation.
<!----------------------------------------------------------------------------->

### 2.3 (4 points)

Now, you should be more familiar with your data, and also have made progress in answering your research questions. Based on your interest, and your analyses, pick 2 of the 4 research questions to continue your analysis in the remaining tasks:

<!-------------------------- Start your work below ---------------------------->

1.  **Of the 8 most common species of cherry trees in Vancouver which one is planted most often? Does the planting of different species change over time and area?** (altered question 4 - slightly by wording for specificity)
2.  **What is the relationship between location and common cherry tree diameter?** (altered question 2)

<!----------------------------------------------------------------------------->

Explain your decision for choosing the above two research questions.

<!--------------------------- Start your work below --------------------------->

1. I chose 1 (altered question 4) because the box plot graph I made in the graphing portion of the question yielded interesting results. It seems as though there is a difference in the type common cherry trees planted over time. It is interesting because it seems like the Schubert Chokecherry wasn't planted very often until around 2010, then it seems to be planted quite a bit. While the Akebono flowering cherry and the Kwanzan flowering cherry seem to be planted at a consistent rate over a long period of time.  

2. I chose 2 (altered question 2) because I would like investigate the data set further using numerical variables and using longitude for the area variable. The graph I produced earlier in this analysis make it seem as though there is a relationship between the two variables. I think that I would like to investigate this relationship further.

<!----------------------------------------------------------------------------->

Now, try to choose a version of your data that you think will be appropriate to answer these 2 questions. Use between 4 and 8 functions that we've covered so far (i.e. by filtering, cleaning, tidy'ing, dropping irrelevant columns, etc.).

(If it makes more sense, then you can make/pick two versions of your data, one for each research question.) 

<!--------------------------- Start your work below--------------------------->
**Question 1**

I used the dplyr function summarise() to get an idea of how many of the tree species were in Vancouver east and Vancouver west. This get me one step closer to seeing if there is a difference in planting data between the two areas by species. 
```{r}
name_area <- cherry_area %>% 
  group_by(area, common_name, date_planted) %>% 
  summarise(Count = n())
print(name_area)
```
Now I am going to look closer at the Schubert Chokecherry as I said that it showed an interesting distribution in the box plot I made earlier in this data analysis. I decided to look at the frequency and number of Schubert chokecherry trees planted by year. I arranged the values in descending order so that years where the most Schubert chokecherry trees were planted were at the top.  
```{r}
freq_cherry <- cher_dat %>%
  group_by(common_name = "SCHUBERT CHOKECHERRY", Year) %>%
  summarise(n = n(), .groups = "drop_last") %>%
  mutate(freq = n / sum(n)) %>% 
  arrange(desc(freq))

print(freq_cherry)
```
Now that I've seen the frequency of planting by year for one particular tree species, I would like to pivot the data wider so that I can see how the planting for each species may differ by year. 
```{r}
new_cher_a <- cher_dat %>% 
  pivot_wider(id_cols = common_name, names_from = Year, values_from = area, 
              values_fn = length)
print(new_cher_a)
```
I can see by looking at the tibble above that there is a lot of planting information (YEAR) missing regarding the 8 most common types of cherry trees in Vancouver.With all the NA columns in the data it would likely be the best to not differentiate by planting year.

I now will pivot the data wider again to look at the planting values arrange for the areas of Vancouver (Vancouver west & Vancouver East).
```{r}
new_cher_b <- cher_dat %>% 
  pivot_wider(id_cols = common_name, names_from = area, values_from = Year, 
              values_fn = length)
print(new_cher_b)
```
The tibble above that I made from pivoting wider shows that the Kwanzan Flowering Cherry was planted by far the most of the 8 types of cherry trees (in both areas).
```{r}
sum_b <- summary(new_cher_b)

print(sum_b)
```
I used a summary function to get more statistics on the 8 most common species of cherry trees planted in Vancouver (in this data set).

**Question 2**
```{r}
new_cher_c <- cher_dat %>% 
  pivot_wider(id_cols = common_name, names_from = diameter, values_from = latitude, 
              values_fn = length)
print(new_cher_c)
```
Above I pivoted the tibble wider to show the diameter measurements of the common cherry trees that have latitude measurements. It seems like it is quite a number of them. Given the abundance of numerical data points I think that question 2 will be good to use in part 3 of this data analysis. 
<!----------------------------------------------------------------------------->

# Task 3: Modelling

## 3.0 (no points)

Pick a research question from 1.2, and pick a variable of interest (we'll call it "Y") that's relevant to the research question. Indicate these.

<!-------------------------- Start your work below ---------------------------->

**Research Question**: **What is the relationship between location and common cherry tree diameter?** (altered question 2)

**Variable of interest**: **Longitude** 

<!----------------------------------------------------------------------------->

## 3.1 (3 points)

Fit a model or run a hypothesis test that provides insight on this variable with respect to the research question. Store the model object as a variable, and print its output to screen. We'll omit having to justify your choice, because we don't expect you to know about model specifics in STAT 545.

-   **Note**: It's OK if you don't know how these models/tests work. Here are some examples of things you can do here, but the sky's the limit.

    -   You could fit a model that makes predictions on Y using another variable, by using the `lm()` function.
    -   You could test whether the mean of Y equals 0 using `t.test()`, or maybe the mean across two groups are different using `t.test()`, or maybe the mean across multiple groups are different using `anova()` (you may have to pivot your data for the latter two).
    -   You could use `lm()` to test for significance of regression coefficients.

<!-------------------------- Start your work below
---------------------------->
I use the lm() function to create a linear regression model. I did this to see what the relationship was between 2 numerical variables (longitude and diameter) in the data. I used the cherry_area subset of my data so that the answer would tell me the relationship between these two variables only for the 8 most common species of cherry trees in Vancouver (as that pertains to the question I am trying to answer).
```{r}
model_cherry <-lm(longitude ~ diameter, cherry_area)

print(model_cherry)
```
<!----------------------------------------------------------------------------->

## 3.2 (3 points)

Produce something relevant from your fitted model: either predictions on Y, or a single value like a regression coefficient or a p-value.

-   Be sure to indicate in writing what you chose to produce.
-   Your code should either output a tibble (in which case you should indicate the column that contains the thing you're looking for), or the thing you're looking for itself.
-   Obtain your results using the `broom` package if possible. If your model is not compatible with the broom function you're needing, then you can obtain your results by some other means, but first indicate which broom function is not compatible.

<!-------------------------- Start your work below ---------------------------->
I chose to use the tidy() function from the `broom` package to view the P value, which would determine if the relationship between x & y (diameter and longitude) is statistically significant or not. Note: I used the summary() function first for my own satisfaction to view the results. 
```{r}
summary(model_cherry)
tidy_model <- tidy(model_cherry)

print(tidy_model)
```
The positive coefficient shows that there is a positive or increasing relationship between the diameter and longitude for the 8 most common cherry trees in Vancouver. 

Using the broom package function tidy() we can see the p.value here is quite small meaning that the regression output is statistically significant. 


<!----------------------------------------------------------------------------->

# Task 4: Reading and writing data

Get set up for this exercise by making a folder called `output` in the top level of your project folder / repository. You'll be saving things there.

## 4.1 (3 points)

Take a summary table that you made from Task 1, and write it as a csv file in your `output` folder. Use the `here::here()` function.

-   **Robustness criteria**: You should be able to move your Mini Project repository / project folder to some other location on your computer, or move this very Rmd file to another location within your project repository / folder, and your code should still work.
-   **Reproducibility criteria**: You should be able to delete the csv file, and remake it simply by knitting this Rmd file.

<!-------------------------- Start your work below ---------------------------->

Above I used the write_csv() function to turn the summary table from Task 1 into a .csv file. I use the here() function to build a path to the cher_dat.csv.
```{r}
here()
head(cher_dat)
write_csv(cher_dat,
          here::here("cher_dat.csv"))

here("cher_dat.csv")
```
<!----------------------------------------------------------------------------->

## 4.2 (3 points)

Write your model object from Task 3 to an R binary file (an RDS), and load it again. Be sure to save the binary file in your `output` folder. Use the functions `saveRDS()` and `readRDS()`.

-   The same robustness and reproducibility criteria as in 4.1 apply here.

<!-------------------------- Start your work below ---------------------------->
To save the model object from task 3 to an R binary file I use the function saveRDS(). I use the here() function to build a path to the model_cherry.rds. This is to replicate the robustness and reproducibility criteria from 4.1.
```{r}
saveRDS(model_cherry, "model_cherry.rds")

here_model <- here("model_cherry.rds")
here(here_model)
```
To read the R binary file I use the readRDS() function. I assign the same name to avoid confusion.
```{r}
model_cherry <- readRDS("model_cherry.rds")

print(model_cherry)
```
<!----------------------------------------------------------------------------->

# Overall Reproducibility/Cleanliness/Coherence Checklist 

Here are the criteria we're looking for.

## Coherence (0.5 points)

The document should read sensibly from top to bottom, with no major continuity errors. 

The README file should still satisfy the criteria from the last milestone, i.e. it has been updated to match the changes to the repository made in this milestone. 

## File and folder structure (1 points)

You should have at least three folders in the top level of your repository: one for each milestone, and one output folder. If there are any other folders, these are explained in the main README.

Each milestone document is contained in its respective folder, and nowhere else.

Every level-1 folder (that is, the ones stored in the top level, like "Milestone1" and "output") has a `README` file, explaining in a sentence or two what is in the folder, in plain language (it's enough to say something like "This folder contains the source for Milestone 1").

## Output (1 point)

All output is recent and relevant:

-   All Rmd files have been `knit`ted to their output md files. 
-   All knitted md files are viewable without errors on Github. Examples of errors: Missing plots, "Sorry about that, but we can't show files that are this big right now" messages, error messages from broken R code
-   All of these output files are up-to-date -- that is, they haven't fallen behind after the source (Rmd) files have been updated.
-   There should be no relic output files. For example, if you were knitting an Rmd to html, but then changed the output to be only a markdown file, then the html file is a relic and should be deleted.

Our recommendation: delete all output files, and re-knit each milestone's Rmd file, so that everything is up to date and relevant.

## Tagged release (0.5 point)

You've tagged a release for Milestone 2. 

### Attribution

Thanks to Victor Yuan for mostly putting this together.
